### 2013-10-07 mr_background.tex
re-organized radical prostatectomy text

\subsubsection{Functional MR Sequences}
Even though T2WI is the mainstay of prostate MR, its overall performance in
prostate cancer diagnosis is not optimal. The incorporation of two or more
functional sequences in multiparametric MR imaging (mpMRI) has been shown to
significantly improve the performance of MRI in cancer
diagnosis.~\cite{Turkbey2012}  The European Society of Urogenital Radiology’s
(ESUR) prostate MR guidelines recommend at least 2 functional imaging
techniques, in addition to T2WI, to better characterize prostate
tumors.~\cite{Barentsz2012} In a study by Turkbey \etal, researchers found that
mpMRI had a PCa detection positive predictive value of 98\%.~\cite{Turkbey2012}
Functional sequences include diffusion-weighted imaging (DWI), dynamic contrast
enhanced imaging (DCE-MRI) and MR spectroscopic imaging (MRSI).  While mpMRI is
critical in improving PCa detection, T2WI is mainstay of delineating prostate
anatomy, and for the purposes of comparing prostate anatomy between ARFI and MR
images, T2WI were used exclusively in this study.

>>>>

\subsubsection{Functional MR Sequences}
Even though T2WI is the mainstay of prostate MR, its overall performance in
prostate cancer diagnosis is not optimal. The incorporation of two or more
functional sequences in multiparametric MR imaging (mpMRI) has been shown to
significantly improve the performance of MRI in cancer
diagnosis.~\cite{Turkbey2012}  The European Society of Urogenital Radiology
(ESUR) prostate MR guidelines recommend at least 2 functional imaging
techniques, in addition to T2WI, to better characterize prostate
tumors.~\cite{Barentsz2012} In a study by Turkbey \etal, researchers found that
mpMRI had a PCa detection positive predictive value of 98\%.~\cite{Turkbey2012}
Functional sequences include diffusion-weighted imaging (DWI), dynamic contrast
enhanced imaging (DCE-MRI) and MR spectroscopic imaging (MRSI).  While mpMRI is
critical in improving PCa detection, T2WI is mainstay of delineating prostate
anatomy, and for the purposes of comparing prostate anatomy between ARFI and MR
images, T2WI were used exclusively in this study.

### 2013-10-07 path_methods.tex
updated with all of the latest data
re-organized radical prostatectomy text

\subsection{Pathology Processing}
After excision, the prostates were weighed and tri-axially measured, formalin
fixed for at least 24 hours without being cut, and then processed for whole
mount histology.  While tri-axial measurements of the gross prostate were not necessarily anatomically aligned, rough estimates of the prostate volume were made using a tri-axial, ellipsoidal organ volume assumption, where the volume could be estimated as:

\begin{equation}
V = \frac{4}{3}\pi \sqrt{\det{A^{-1}}},
\end{equation}

>>>>

\subsection{Pathology Processing}
Prostates were radically removed using a da Vinci Surgical System (Intuitive
Surgical\textregistered, Inc., Sunnyvale, CA).  After excision, the prostates
were weighed and tri-axially measured, formalin fixed for at least 24 hours
without being cut, and then processed for whole mount histology.  While
tri-axial measurements of the gross prostate were not necessarily anatomically
aligned, rough estimates of the prostate volume were made using a tri-axial,
ellipsoidal organ volume assumption, where the volume could be estimated as:

\begin{equation}\label{eqn:ellipsoid_volume}
V = \frac{4}{3}\pi \sqrt{\det{A^{-1}}},
\end{equation}
